DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-02 paper/overview.tex
caption in Figure 3.

\begin{figure}[h]
  \centering
  \includegraphics[width=.4\textwidth]{figs/architecture}
  \caption{DeepPicar's neural network architecture: 9 layers (5
    convolutional, 4 fully-connected layers), 250K
    parameters. Adopted from ~\cite{Bojarski2016}.}
  \label{fig:architecture}
\end{figure}

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=.4\textwidth]{figs/architecture}
  \caption{DeepPicar's neural network architecture: 9 layers (5
    convolutional, 4 fully-connected layers), 27 million connections,
    250K parameters. The architecture is identical to the one used
    in~\cite{Bojarski2016}.}
  \label{fig:architecture}
\end{figure}
